---
title: "Package installation"
date: "`r format(Sys.time(), '%H:%M %d %B %Y ')`"
---

- Please make sure *if at all possible* that you have the latest version of R installed (3.2.3)
- An up-to-date version of RStudio is strongly recommended, unless you have a programming environment that you prefer.
- Try to install the `core` and `extra0` packages below. If you can, install the extras, but don't worry if you run into trouble; I went a little bit nuts including almost any package that I ever use for mixed modeling or related tasks ... in particular you should make sure you have `lme4` version 1.1-10.

First update your current packages:

```{r update,eval=FALSE}
update.packages()
```

Now install a whole bunch of new ones, as necessary.

```{r pkglist}
core_pkgs <- c("lme4","lmerTest","MCMCglmm","pbkrtest","blme","ordinal")
extra0_pkgs <- c("ggplot2","broom","dotwhisker","coda","devtools", "car")
extra1_pkgs <- c("afex", "agridat", "AICcmodavg", "aods3", "arm", "bbmle",
                "benchmark", "cAIC4", "dplyr", "effects", "emdbook", "gamm4",
                "GGally", "ggplot2", "glmmLasso", "glmmML", "gridExtra", "hglm",
                "HLMdiag", "Hmisc", "influence.ME", "knitr", 
                "lqmm", "lsmeans", "MEMSS", "metafor", "mlmRev",
                "multcomp", "MuMIn", "numDeriv",
                "pedigreemm", "plotMCMC", "plotrix", "plyr", "R2admb",
                "reshape2", "RLRsim", "rmarkdown", "robustlmm", "rockchalk",
                "SASmixed", "simr", "sjPlot", "stargazer", "texreg","TMB")
extra2_pkgs <- c("spaMM","R2jags","rstanarm","brms")
```

```{r rgraphviz,eval=FALSE,echo=FALSE}
## Rgraphviz is only on Bioconductor now ...
## don't use dependencies=TRUE (!)
i1 <- installed.packages()
r1 <- lapply(as.data.frame(i1)[c("Depends","Suggests","LinkingTo","Enhances")],
       grep,pattern="Rgraphviz",ignore.case=TRUE)
i1[unlist(r1),"Package"]
## use http:// if https:// is problematic
source("https://bioconductor.org/biocLite.R")
biocLite("Rgraphviz")
```

```{r get_new}
## install packages if not already installed
get_new_pkgs <- function(pkgs,...) {
    i1 <- installed.packages()
    new_pkgs <- setdiff(pkgs,i1[,"Package"])
    if (length(new_pkgs)>0)
        install.packages(new_pkgs,...)
}
for (pkg_list in list(core_pkgs,extra0_pkgs,extra1_pkgs,extra2_pkgs)) {
    get_new_pkgs(pkg_list)
}
```

## Off-CRAN packages

These packages are useful for some more advanced modeling, especially in ecology ... installation is optional.

### INLA

```{r inla,eval=FALSE}
source("http://www.math.ntnu.no/inla/givemeINLA.R")
```

### `glmmADMB`

```{r glmmADMB,eval=FALSE}
install.packages("glmmADMB",
                 type="source",
                 repos=c("http://glmmadmb.r-forge.r-project.org/repos",
                         getOption("repos")))
```

### `glmmTMB`

```{r glmmTMB,eval=FALSE}
devtools::install_github("glmmTMB/glmmTMB",sub="glmmTMB")
```

